Notes & Ideas

### 2018-11-30 course_notes.Rmd
update

*record.id*  
>Column is a semester ID and 5-digit number, like sp18.00001. This particular record.id indicates the data line is from Spring 2018 CSV file, and is line 00001 of the data table. This should be the unique primary key value for each record. Once assigned, it should not change.

*report.id*  
>Format is R\_nnn(...). The string is assigned to each entry made in Qualtrics. This particular string is assigned when a report is collected by our system. It is anonymous, and serves as a unique id for each REPORT document that we collect.

*student*  
>The email address of the SUBMITTING STUDENT. Unique to each student, and assigned by WFU. The email address connects multiple reports to a SINGLE STUDENT AUTHOR. It is NOT confidential though, so needs to be switched out.

*ta*  
>The name of the TA assigning scores. Unique to instructor, and connects multiple reports scored by SINGLE TA. Again it is NOT confidential, so also needs to be switched out.

>>>>

*record.id*

>Column is a semester ID and 5-digit number, like sp18.00001. This particular record.id indicates the data line is from Spring 2018 CSV file, and is line 00001 of the data table. This should be the unique primary key value for each record. Once assigned, it should not change.

*report.id*

>Format is R\_nnn(...). The string is assigned to each entry made in Qualtrics. This particular string is assigned when a report is collected by our system. It is anonymous, and serves as a unique id for each REPORT document that we collect.

*student*

>The email address of the SUBMITTING STUDENT. Unique to each student, and assigned by WFU. The email address connects multiple reports to a SINGLE STUDENT AUTHOR. It is NOT confidential though, so needs to be switched out.

*ta*

>The name of the TA assigning scores. Unique to instructor, and connects multiple reports scored by SINGLE TA. Again it is NOT confidential, so also needs to be switched out.
